The LBRY Trending Algorithm

### 2021-11-18 tex/ms.tex
New figure

Instead of $\log$, define a squashing function $S$ as:
\begin{align}
S(x) &=
    \left\{
        \begin{array}{lr}
            \log (1 + x), & \textnormal{if } x \geq 0, \\
            -\log(1 - x), & \textnormal{otherwise}.
        \end{array}
    \right.
\end{align}
The inverse, unsquashing function, is
\begin{align}
U(x) = S^{-1}(x) &=
    \left\{
        \begin{array}{lr}
            \exp(x) - 1,  & \textnormal{if } x \geq 0, \\
            1 - \exp(-x), & \textnormal{otherwise}.
        \end{array}
    \right.
\end{align}
For large positive values, these are approximately equal to log and exp
respectively, but for smaller values (and negative values), it remains
continuous.

>>>>

Instead of $\log$, define a squashing function $S$ as:
\begin{align}
S(x) &=
    \left\{
        \begin{array}{lr}
            \log (1 + x), & \textnormal{if } x \geq 0, \\
            -\log(1 - x), & \textnormal{otherwise}.
        \end{array}
    \right.
\end{align}
The inverse, unsquashing function, is
\begin{align}
U(x) = S^{-1}(x) &=
    \left\{
        \begin{array}{lr}
            \exp(x) - 1,  & \textnormal{if } x \geq 0, \\
            1 - \exp(-x), & \textnormal{otherwise}.
        \end{array}
    \right.
\end{align}
For large positive values, these are approximately equal to log and exp
respectively, but for smaller values (and negative values), it remains
continuous --- see Figure~{fig:squash}.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\textwidth]{figures/squash.pdf}
\caption{The squashing function $S(x)$ is the solid black curve.
The dashed blue and pink curves are $\log(x)$ and $-\log(-x)$ respectively.
\label{fig:squash}}
\end{figure}
